%%-*-latex-*-

\documentclass[a4paper,11pt]{article}

\usepackage[british]{babel} % British English
\usepackage[T1]{fontenc}    % Required for hyphenation
\usepackage{url}            % Typesets URLs
\usepackage{xspace}         % Adds space after macro expansions if needed
\usepackage{hyphenat}       % Hyphenation of compounded words
\usepackage{mdwlist}        % Tight vertical spacing of list items
\frenchspacing              % Settles the tricky business with \@

\newcommand{\cpp}{\mbox{C \hspace*{-2.5mm} \raise 0.7mm \hbox{${\scriptscriptstyle ++}$}}}

\begin{document}

\begin{center}
\textbf{\LARGE Dr Christian Rinderknecht}\\[5mm]
       {\large Theory of Programming Languages, Compiler Construction,
         Blockchains, Virtual Machines, Domain\hyp{}Specific
         Languages, Functional Languages, Formal Methods}
\end{center}

\noindent
\begin{tabular}{@{}l@{\qquad\qquad\qquad\qquad}r@{}}
  Christian Rinderknecht
& \url{http://github.com/rinderknecht}\\
  Széchenyi István utca, 8
& \texttt{+36 70 311 6130}\\
  3300 Eger, \textsc{Hungary}
& \url{rinderknecht@free.fr}
\end{tabular}

\medskip

\noindent{\small\url{https://www.linkedin.com/in/christian-rinderknecht-19342147}}

\pagestyle{empty}

\bigskip
\noindent\textbf{\large Key skills and knowledge}
\begin{itemize*}

  \item College professor and researcher
    (\oldstylenums{2001}-\oldstylenums{2014})

  \item International work experience (France, Korea, Hungary, Sweden)

  \item Theory of programming languages and functional languages

  \item Interpreter and compiler construction

  \item Smart contract languages and Virtual Machines for blockchains

%  \item Multidisciplinary engineering (SE, telecom, electronics, mechanics)

  \item Protocol engineering and model-based test generation

  \item Technical documentation and scholarly publications (papers, books)

  \item Bilingual French/Spanish and fluent English (C1 level 93\%)

\end{itemize*}

\smallskip
\noindent\textbf{\large Employment History}
\bigskip

\noindent\textbf{2023-} \ \textsf{Turnstiles Kft.} (Budapest,
Hungary)\\ \ \ \ \ \emph{Founder}\\
Freelance expert in compilers, program transformations, static
analysis, logic systems (syntax and semantics ---~the two turnstile
symbols).

\bigskip

\noindent\textbf{2018-2025} \ \textsf{LIGO} (Paris,
London)\\ \ \ \ \ \emph{COO of LIGOlang \& Compiler Engineer}\\ Design
of the high-level smart contract language LIGO for the blockchain
Tezos and lead dev on the compiler front-end of LIGO in OCaml.

\bigskip

\noindent\textbf{2017-2018} \ \textsf{GrAI Matter Labs} (Paris,
France)\\ \ \ \ \emph{Compiler Engineer}\\ Design of a Domain-Specific
Language for describing a new kind of computational
neuromorphic spiking network, and implementation of a standalone
interpreter and a transpiler to OCaml to build the networks.

\bigskip
%\newpage

\noindent\textbf{2016} \ \textsf{Wolfram | MathCore}
(Link\"oping, Sweden)\\ \ \ \ \emph{Compiler Engineer}\\ Design and
implementation in OCaml of a correct and complete set of parsers
for the Modelica compiler of Wolfram SystemModeler, featuring a
precise, correct and complete set of syntax errors.

\bigskip

\noindent\textbf{2014-2015} \ \textsf{Cortus}, \textsf{Numalis}
(Montpellier, France)\\ \ \ \ \emph{Compiler Engineer}\\ Maintenance
and development of a .NET compiler (in C$^\sharp$ and
OCaml). Development of tools in \cpp{} and OCaml for assessing the
loss of accuracy in floating-point calculations by means of
source\hyp{}to\hyp{}source transformations (standalone and based on
Clang/LLVM) of \cpp{} code.

\bigskip

\noindent\textbf{2001-2014} \ \textsf{\emph{Researcher and University
  Professor}} (France, Korea, Hungary)\\ \ \ \ \emph{Professor \&
Researcher} (Information and Communications University, École
Supérieure d'Ingénieurs Léonard de Vinci, Konkuk University, Eötvös
Loránd University)\\ Teaching of programming (OCaml, Prolog, Erlang,
XSLT, C/\cpp, Pascal, Java), software engineering, internet protocols,
algebraic specifications, automata theory, parsing theory, static
program transformations etc. Scholarly publications on compiler
construction, protocol verification, domain\hyp{}specific language
design, didactic of programming languages, functional programming and
mathematical analysis of algorithms (book).

\bigskip

\noindent\textbf{2000} \ \textsf{PolySpace Tech.\@} (now MathWorks,
Montbonnot, France)\\ \emph{Compiler Engineer}\\ Development of a static
analyser for JavaCard, automatic testing, reverse\hyp{}engineering and
maintenance, case studies and sales support.

\bigskip

\noindent\textbf{1998-2000} \ \textsf{National Institute of
  Telecommunications} (now T\'el\'ecom SudParis)\\ \emph{R\&D
  Engineer} (Software for Networking Lab.)\\ R\&D projects,
specification-based test generation for telecommunication services,
development of tools for protocol testing. Scholarly publications.

\bigskip

\noindent\textbf{1997-98} \ \textsf{Alcatel-Alsthom CRC} (now
Alcatel-Lucent R\&I, France)\\ \emph{Case Engineer} (Object
Architecture Unit)\\ Design of a software quality analysis for a
\cpp{} project (networking).

\bigskip
\noindent\textbf{\large Education}
\bigskip

\noindent\textbf{1993-98} \ \textsf{INRIA \& Pierre and Marie Curie
  University} (France)\\ \emph{Ph.D.\@ in Informatics (cum
laude)}\\ Theory of programming languages. Formalisation of ASN.1,
design and implementation of the front-end of an ASN.1 compiler in
OCaml. Soundness proof of the Basic Encoding Rules (BER). Working
group at ISO on ASN.1 (London, \oldstylenums{1997}).

%% \bigskip
%% \noindent\textbf{\large Languages and Tools}
%% \medskip
%% \begin{itemize*}

%%   \item Strong background in theory of programming.

%%   \item Programming languages: OCaml, Java, Erlang,
%%     C$^\sharp$, \cpp, XSLT, Ada, Standard ML, Prolog, Pascal.

%  \item Tools: Emacs, Make, dune, git, shell, scanning and
%    parsing (sed, ocamllex, menhir, tree-sitter) etc.

%  \item Markup languages: \LaTeX, XML, DTD, Markdown, JSON etc.

%  \item \textit{Protocol engineering}: ObjectGeode, Tau (Telelogic),
%    LOTOS, ASN.1, TTCN-3, MSC, SDL, specification-based test
%    generation, automata theory.

  %% \item \textit{Software engineering}: Test generation, compiler
  %%   construction, static analysis, program transformations, formal
  %%   methods (specification, correctness) %, Docker Engine/Machine.

%  \item \textit{System administration}: Linux, OS~X.

%  \item \textit{Databases}: SQLite.

%  \item \textit{Free Software}: \url{http://github.com/rinderknecht}

%%     Shell scripts for Linux system
%%     administration, a pretty\hyp{}printer for \TeX{} messages, a build
%%     system for OCaml, an OCaml library for dictionaries based on
%%     ternary search trees, a preprocessor for C$^\sharp$.

%\end{itemize*}

\newpage
%\bigskip
\noindent\textbf{\large Publications, Honours and Miscellanea}

\bigskip

\noindent Informatics:
\begin{itemize*}

  \item Fifteen (15) papers in journals and conferences, three (3)
    extensive technical reports.

  \item \textit{Design and Analysis of Purely Functional Programs}
    (volume 15, \emph{Texts in Computing}, College Publications, UK,
    Nov~\oldstylenums{2012}, Third Edition \oldstylenums{2025},
    \oldstylenums{598}~pages). I translated my book into French for
    the same publisher: \textit{Conception et analyse des programmes
      purement fonctionnels} (volume 12, \emph{Cahiers de Logique et
    d'Épistémologie}, \oldstylenums{2012}).

  \item One of my mathematical articles is the source for the integer
    sequence \url{http://oeis.org/A261003}.

  \item I received a cheque from Knuth for finding an error in
    Volume~\oldstylenums{4} of \emph{The Art of Computer Programming}.

\end{itemize*}

\noindent Literature \& Music:
\begin{itemize*}

  \item Translator from Spanish to French of \textit{Vingt poèmes
    d'amour et une chanson désespérée} by Pablo Neruda (Gallimard
    Poésie, Paris, \oldstylenums{1998}).

  \item Contributor of Buddhist vocabulary to the \emph{Sanskrit
  Heritage} (French-Sanskrit dictionary, \oldstylenums{1998}) of
    Gérard Huet\\ (\url{http://sanskrit.inria.fr/Heritage.pdf}).

  \item Editor and translator from French to Spanish of an anthology
    of the poetry of Paul Valéry, \emph{Las granadas} (Ediciones
    Rilke, Madrid, \oldstylenums{2016}).

  \item Editor and translator from Spanish to French of the complete
    poetry of Gustavo Adolfo B\'ecquer, \textit{Rimes} (L'Harmattan,
    Paris, \oldstylenums{2024}).

  \item Publisher of my own poetry (\textit{Running on}) in English
    (\oldstylenums{2024}).

  \item Working nowadays on an anthology and translation from
    Hungarian to English, French and Spanish of the poetry of József
    Attila.

  \item Cello player (Baroque \emph{piccolo cello}).

\end{itemize*}

\bibliographystyle{unsrt}
\bibliography{cv_rinderknecht}
\nocite{*}

\end{document}
