  %-*-latex-*-

\documentclass[a4paper,11pt]{article}

% Language and fonts
%
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage{hyphenat}
\usepackage{url}

\pagestyle{empty}

\begin{document}

\noindent
\begin{tabular}{@{}l@{\qquad\qquad\qquad}r@{}}
  Christian \textsc{Rinderknecht}
  & \\
  Széchenyi István utca, 8
  & \\
  3300 Eger, Hungary \\
  \texttt{+36 70 311 6130} \\
  \url{rinderknecht@free.fr}
\end{tabular}

\bigskip

\begin{center}
  \large Cover letter
\end{center}

\bigskip

After my doctorate in informatics, I worked as an engineer in
companies, but also as a professor in universities until
\oldstylenums{2014} (ELTE in Budapest was the last). During those
years, I taught in English, in several countries; I got to learn about
many cultures; I published thousands of pages in English, and hundreds
in French.

Next to my career in informatics, I cultivated my passion for the
translation of poetry, starting with Pablo Neruda in
\oldstylenums{1998}, published by Gallimard. Since then I have
published several more translations, mostly from French to Spanish or
vice\hyp{}versa, but also, this year, from Hungarian to French,
English and Spanish (poetry by Attila József). I do not speak
Hungarian yet, and I will study it further. Furthermore, I also
published my own poems in English.

I wish to change career and return to education, literature and
languages. I taught French and Spanish in private, and I would like to
work nowadays within a school.

I own a Hungarian company (Kft) and I can therefore invoice for my
services, but I would also be open to becoming an employee.

\bigskip
\bigskip

\hfill Written in Eger, \oldstylenums{28} April \oldstylenums{2026}.

\bigskip
\bigskip
\bigskip
\bigskip
\hfill Christian Rinderknecht

\bigskip

\end{document}
